---
title: "Christmas Dinner"
author: "RPDearden"
date: "08/11/2018"
output: html_document
runtime: shiny
---
```{r setup, include=FALSE, warnings=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(shinyTime)
library(tidyverse)
library(lubridate)
```

The first aim of this document is for me to learn how to use Shiny.  The second is to allow me to calculate my Christmas Dinner quantities and timetable.  It is a work in progress.

Turkey deets are taken from [here](https://www.theguardian.com/lifeandstyle/wordofmouth/2010/dec/20/how-to-cook-perfect-christmas-dinner)

## Dinner Details

```{r dinner_inputs, echo=FALSE, warnings=FALSE}
inputPanel(
  numericInput("TurkeyWeight", label = "Weight of turkey (g)", 
               value = 450, min = NA, max = NA, step = NA),
  numericInput("BumsOnSeats", label = "Number of people",
               value =6, min = 1, max = NA, step = 1),
  sliderInput("DinsTime", label="Dinner time",
              min=0, max=24, value=14, post=":00")
)
```


## Turkey
Taken from [here](https://www.theguardian.com/lifeandstyle/wordofmouth/2010/dec/20/how-to-cook-perfect-christmas-dinner), which has the recipe

To make your turkey you will require:

* 1 turkey, of weight above, with giblets

* 170g butter

* half an onion

* bay leaf

* piece of cook's muslin

For gravy:

* 1 tbsp plain flour

* 4tbsp madeira

* 568ml hot poultry stock or water


```{r turkey_outputs, echo=FALSE}

renderText({
  TurkeyTime <- ((((input$TurkeyWeight)/450)*20)+20)
  HMSTurkTime <- seconds_to_period(TurkeyTime*60)
  paste("You will need to cook your turkey for", TurkeyTime, "minutes")
})
```

##Potatoes
Rather than being boiled, mashed, or stuck in a stew these are roasted from [here](https://www.theguardian.com/lifeandstyle/wordofmouth/2010/dec/20/how-to-cook-perfect-christmas-dinner)

*n.b. need to sort out dem decimals*

```{r potato_outputs, echo=FALSE}

renderText({
  paste("-",(((input$BumsOnSeats)/6)*1.2), "kg potatoes")
})
renderText({
  paste("- A jar of goose fat OR",(((input$BumsOnSeats)/6)*4),"tbsp olive oil")
})
```


##Timetable
```{r timetable_outputs, echo=FALSE}

renderTable({
  hrs <- function(u) {
  x <- u * 3600
  return(x)
  }
  mns <- function(m) {
   x <- m * 60
   return(x)
  }
  
  TurkeyTime <- ((((input$TurkeyWeight)/450)*20)+20)
  HMSTurkTime <- seconds_to_period(TurkeyTime*60)
  Dinnertime1 <- strptime(input$DinsTime, format="%H")
  Dinnertime2 <- paste(hour(Dinnertime1),":00", sep="")
  TurkeyStand1 <- Dinnertime1 - mns(30)
  TurkeyStand2 <-paste(hour(TurkeyStand1),minute(TurkeyStand1), sep=":")
  CookTurkey1 <- TurkeyStand1 - HMSTurkTime
  CookTurkey2 <-paste(hour(CookTurkey1),minute(CookTurkey1), sep=":")
  PrepTurkey1 <- CookTurkey1 - hrs(1)
  PrepTurkey2 <-paste(hour(PrepTurkey1),minute(PrepTurkey1), sep=":")
  
things <- tribble(
 ~Task,            ~Start,  ~End,    ~Category,
 "Prepare Turkey", PrepTurkey2, CookTurkey2, "Prep",
 "Cook Turkey",    CookTurkey2, TurkeyStand2, "Cooking",
 "Turkey Stands",  TurkeyStand2, Dinnertime2, "Misc"
)

  })

#GANTT chart plots below
renderPlot({
  hrs <- function(u) {
  x <- u * 3600
  return(x)
  }
  mns <- function(m) {
   x <- m * 60
   return(x)
  }
   TurkeyTime <- ((((input$TurkeyWeight)/450)*20)+20)
  HMSTurkTime <- seconds_to_period(TurkeyTime*60)
  Dinnertime1 <- strptime(input$DinsTime, format="%H")
  Dinnertime2 <- paste(hour(Dinnertime1),":00", sep="")
  TurkeyStand1 <- Dinnertime1 - mns(30)
  TurkeyStand2 <-paste(hour(TurkeyStand1),minute(TurkeyStand1), sep=":")
  CookTurkey1 <- TurkeyStand1 - HMSTurkTime
  CookTurkey2 <-paste(hour(CookTurkey1),minute(CookTurkey1), sep=":")
  PrepTurkey1 <- CookTurkey1 - hrs(1)
  PrepTurkey2 <-paste(hour(PrepTurkey1),minute(PrepTurkey1), sep=":")
   
  
  plot(1)

  
  
})

```
GANNT chart cobbled together with considerable inspiration from [here](https://insileco.github.io/2017/09/20/gantt-charts-in-r/)